Peridynamic Beams: \\ A Non-ordinary, State Based Model

### 2014-02-06 BeamPaper.tex
diagrams and brittle plots prettied up

\subsection{Weighting Function and Perfect Plasticity}
\label{sec:WeightFunction}
The weighting function \(\omega(\xi)\) describes the relative contribution of each bond-pair, and can be defined according to physical or mathematical considerations. 
Consider an Euler beam in bending with curvature \(\kappa\). 
Fibers running parallel to the neutral axis of the beam are stretched in proportion to their distance from the neutral axis, with strain \(\epsilon = y\kappa\). 
If the fibers are linearly elastic, then the axial stress at each location is \(\sigma = E\epsilon = Ey\kappa\), and the contribution to supported moment \(dM = \kappa E y^2 dA\). 
By comparing the formulations for the moments carried by the Euler beam in \cref{fig:EulerBending} and those of the bond-pair beam in \cref{fig:BPBending}, we see some definite parallels.
%
\begin{figure}[h]
\subinputfrom{\diagrampath}{EulerBending.eps_tex}
\caption{Euler beam moment contribution}
\label{fig:EulerBending}
\end{figure}
%%
\begin{figure}[h]
\subinputfrom{\diagrampath}{BondPairBending.eps_tex}
\caption{Bond-pair moment contribution}
\label{fig:BPBending}
\end{figure}
%
\begin{align}
M_\text{classical}&=\int_{-\frac{t}{2}}^{\frac{t}{2}} \sigma \; y \; dA && = \int_{-\frac{t}{2}}^{\frac{t}{2}} E \kappa \; y^2 \; b(y) dy\notag \\
%
M_\text{PD}&=\int_{-\delta}^{\delta} \vstate{T}{}{\xi}\; \xi \; d\xi & = \int_{-\delta}^{\delta} \alpha \frac{\sin(\Delta\theta)}{|\xi|} \; \xi \; \omega(\xi) d\xi\: & \approx \int_{-\delta}^{\delta} \alpha \kappa |\xi| \; \omega(\xi) d\xi\notag
\end{align}
%
The term \(y\) is the distance from the beam's neutral axis and \(b(y)\) is the width of the beam at that distance from the neutral axis. 
The similarity between classical and peridynamic moment formulations suggests a possible formulation for the weighting function:
%
\begin{equation}
\omega(\xi) = |\xi| b\left(y\right) \text{at}\; y=\frac{\xi}{\delta} \frac{t}{2}\notag
\end{equation}
%
\begin{figure}[h]
\minipage[t]{0.5\textwidth}
 \centering
  \subinputfrom{\diagrampath}{WeightProfile_Uniform.eps_tex}
\caption{Weight function for a beam of rectangular cross-section}
\label{fig:WeightProfileUniform}
\endminipage\hfill
\minipage[t]{0.5\textwidth}%
  \centering
  \subinputfrom{\diagrampath}{WeightProfile_Ibeam.eps_tex}
\caption{Weight function for an I-beam}
\label{fig:WeightProfileIbeam}
\endminipage
\end{figure}
%
This weight function analogizes the relative contributions of bond pairs of different lengths to the relative contributions of fibers at different distances from the centerline. 
Examples are shown in \cref{fig:WeightProfileUniform,fig:WeightProfileIbeam}.
While this weighting function offers no advantages over a uniform weight function in the case of the linearly elastic beam, it offers a way to model advancing plasticity.

@@

\begin{figure}[h]
  \centering
  \scalebox{.65}{\input{\plotpath/elastic_h20_g2000_edit.pgf}}
  \caption{The uniform-load elastic beam is accurately modeled with few nodes}
  \label{fig:elastic_g2000}
\end{figure}

As an elastic-perfectly-plastic beam exceeds the elastic limit of its material, plastic zones begin to grow on the top and bottom of the beam's cross section.
This behavior is mimicked by the plasticity of the longest bond-pairs, producing the results shown in \cref{fig:eppu_h10_g2000}.
To accurately capture this phenomenon and model beam plasticity, a finer discretization is required.
\begin{figure}[h]
  \centering
  \scalebox{.65}{\input{\plotpath/eppu_h10_g2000_edit.pgf}}
  \caption{The elastic perfectly-plastic beam requires finer discretization}
  \label{fig:eppu_h10_g2000}
\end{figure}

A material that is plastically deformed does not return to its original state when unloaded.
For a beam in bending, the residual deformations can be seen in a beam that has been loaded beyond the onset of plastic deformation and then unloaded.
This result is observed in the bond-pair plasticity model, shown in \cref{fig:ResidualPlasticity}. 
Accurate residual deformation modeling requires both a relatively small horizon and a fairly large number of nodes.

%
\begin{figure}[h]
\minipage[t]{0.5\textwidth}
 \centering
  \scalebox{.45}{\input{\plotpath/unloaded2_h10_g2000_n.pgf}}
\caption{N-convergence}
\label{fig:ResidualPlasticityN}
\endminipage\hfill
\minipage[t]{0.5\textwidth}%
  \centering
  \scalebox{.45}{\input{\plotpath/unloaded2_n1000_g2000_h.pgf}}
\caption{H-convergence}
\label{fig:ResidualPlasticityH}
\endminipage
\end{figure}

It is more difficult to verify the brittle material model because brittle failure is unstable.
When a crack begins, moment is transferred to other bond pairs, and failure progresses creating a plastic hinge.
This is borne out by the results in \cref{fig:brittleBeam}, in which ``Nodal Health'' represents the fraction of bond-pairs about each node that have not failed.

>>>>

\subsection{Weighting Function and Perfect Plasticity}
\label{sec:WeightFunction}
The weighting function \(\omega(\xi)\) describes the relative contribution of each bond-pair, and can be defined according to physical or mathematical considerations. 
Consider an Euler beam in bending with curvature \(\kappa\). 
Fibers running parallel to the neutral axis of the beam are stretched in proportion to their distance from the neutral axis, with strain \(\epsilon = y\kappa\). 
If the fibers are linearly elastic, then the axial stress at each location is \(\sigma = E\epsilon = Ey\kappa\), and the contribution to supported moment \(dM = \kappa E y^2 dA\). 
By comparing the formulations for the moments carried by the Euler beam in \cref{fig:EulerBending} and those of the bond-pair beam in \cref{fig:BPBending}, we see some definite parallels.
%
\begin{figure}[h]
\subinputfrom{\diagrampath}{EulerBending.eps_tex}
\caption{Euler beam moment contribution}
\label{fig:EulerBending}
\end{figure}
%%
\begin{figure}[h]
\subinputfrom{\diagrampath}{BondPairBending_edit.eps_tex}
\caption{Bond-pair moment contribution}
\label{fig:BPBending}
\end{figure}
%
\begin{align}
M_\text{classical}&=\int_{-\frac{t}{2}}^{\frac{t}{2}} \sigma \; y \; dA && = \int_{-\frac{t}{2}}^{\frac{t}{2}} E \kappa \; y^2 \; b(y) dy\notag \\
%
M_\text{PD}&=\int_{-\delta}^{\delta} \vstate{T}{}{\xi}\; \xi \; d\xi & = \int_{-\delta}^{\delta} \alpha \frac{\sin(\Delta\theta)}{|\xi|} \; \xi \; \omega(\xi) d\xi\: & \approx \int_{-\delta}^{\delta} \alpha \kappa |\xi| \; \omega(\xi) d\xi\notag
\end{align}
%
The term \(y\) is the distance from the beam's neutral axis and \(b(y)\) is the width of the beam at that distance from the neutral axis. 
The similarity between classical and peridynamic moment formulations suggests a possible formulation for the weighting function:
%
\begin{equation}
\omega(\xi) = |\xi| b\left(y\right) \text{at}\; y=\frac{\xi}{\delta} \frac{t}{2}\notag
\end{equation}
%
\begin{figure}[h]
\minipage[t]{0.5\textwidth}
 \centering
  \subinputfrom{\diagrampath}{WeightProfile_Uniform.eps_tex}
\caption{Weight function for a beam of rectangular cross-section}
\label{fig:WeightProfileUniform}
\endminipage\hfill
\minipage[t]{0.5\textwidth}%
  \centering
  \subinputfrom{\diagrampath}{WeightProfile_Ibeam.eps_tex}
\caption{Weight function for an I-beam}
\label{fig:WeightProfileIbeam}
\endminipage
\end{figure}
%
This weight function analogizes the relative contributions of bond pairs of different lengths to the relative contributions of fibers at different distances from the centerline. 
Examples are shown in \cref{fig:WeightProfileUniform,fig:WeightProfileIbeam}.
While this weighting function offers no advantages over a uniform weight function in the case of the linearly elastic beam, it offers a way to model advancing plasticity.

@@

\begin{figure}[h]
  \centering
  \scalebox{.6}{\input{\plotpath/elastic_h20_g2000.pgf}}
  \caption{The uniform-load elastic beam is accurately modeled with few nodes}
  \label{fig:elastic_g2000}
\end{figure}

As an elastic-perfectly-plastic beam exceeds the elastic limit of its material, plastic zones begin to grow on the top and bottom of the beam's cross section.
This behavior is mimicked by the plasticity of the longest bond-pairs, producing the results shown in \cref{fig:eppu_h10_g2000}.
To accurately capture this phenomenon and model beam plasticity, a finer discretization is required.
\begin{figure}[h]
  \centering
  \scalebox{.6}{\input{\plotpath/eppu_h10_g2000.pgf}}
  \caption{The elastic perfectly-plastic beam requires finer discretization}
  \label{fig:eppu_h10_g2000}
\end{figure}

A material that is plastically deformed does not return to its original state when unloaded.
For a beam in bending, the residual deformations can be seen in a beam that has been loaded beyond the onset of plastic deformation and then unloaded.
This result is observed in the bond-pair plasticity model, shown in \cref{fig:ResidualPlasticityN,fig:ResidualPlasticityH}. 
Accurate residual deformation modeling requires both a relatively small horizon and a fairly large number of nodes.

%
\begin{figure}[h]
  \centering
  \scalebox{.6}{\input{\plotpath/unloaded2_h10_g2000_n.pgf}}
  \caption{The need for fine discretization is even more apparent when representing residual plastic deformation}
  \label{fig:ResidualPlasticityN}
\end{figure}
%
\begin{figure}[h]
  \centering
  \scalebox{.6}{\input{\plotpath/unloaded2_n1000_g2000_h.pgf}}
  \caption{Accurately modeling residual plastic deformation also requires a small horizon}
  \label{fig:ResidualPlasticityH}
\end{figure}
%
%\begin{figure}[h]
%\minipage[t]{0.5\textwidth}
% \centering
%  \scalebox{.45}{\input{\plotpath/unloaded2_h10_g2000_n.pgf}}
%\caption{N-convergence}
%\label{fig:ResidualPlasticityN}
%\endminipage\hfill
%\minipage[t]{0.5\textwidth}%
%  \centering
%  \scalebox{.45}{\input{\plotpath/unloaded2_n1000_g2000_h.pgf}}
%\caption{H-convergence}
%\label{fig:ResidualPlasticityH}
%\endminipage
%\end{figure}

It is more difficult to verify the brittle material model because brittle failure is unstable.
When a crack begins, moment is transferred to other bond pairs, and failure progresses until every pair of bonds surrounding a node are broken, creating a hinge at that node.
This is borne out by the results in \cref{fig:brittleBeam}, in which ``Nodal Health'' represents the fraction of bond-pairs about each node that have not failed.
